### 2014-08-04 paper/paper.tex
Fixed the results for the maximum entropy classifier. Filled out the tables

@@

The baseline for this project is established by running the Maximum Entropy
classifier without any stopword removal, uncommon word removal, Or feature
normalization. The F-score that is achieved is 50.72. See Experiment \textit{g}
in Table \ref{table:maxent-results} to see the results in context.

Number of features retained varies from Tweet to Tweet. To summarize the number
of features retained after different process Table \ref{table:numfeatures}
presents the mean number of features per Tweet for positive, neutral, negative
examples as well as an overall average.

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|c||r|r|r|r|r|}
        \hline
        Description        & Positive & Neutral & Negative & Overall & Total \\
        \hline
        All                & 14.85    & 14.06   & 15.10    & 14.49   & 5964 \\
        Just Stopwords     & 15.95    & 15.40   & 16.33    & 15.73   & 0 \\
        Just Uncommon      & 18.54    & 17.81   & 18.82    & 18.22   & 5993 \\
        Just Normalization & 19.64    & 19.15   & 20.05    & 19.46   & 0 \\
        Baseline           & 20.65    & 20.45   & 20.96    & 20.58   & 0 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{`Positive', `Neutral', `Negative', and `Overall' refer to the
    average number of features per Tweet in each experiment. `Total' refers to
    the total number of different features in the dataset}
    \label{table:numfeatures}
\end{table}

@@

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r||c|c|}
        \hline
           Description    & mean F & std F \\
        \hline
           All            & 0.0    & 0.0   \\
           Just Stopwords & 0.0    & 0.0   \\
           Just Uncommon  & 0.0    & 0.0   \\
           Just Normalize & 0.0    & 0.0   \\
           Baseline       & 0.0    & 0.0   \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Performance of the Maximum Entropy classifier using exhaustive
    cross-validation with 5 partitions}
    \label{table:maxent-results}
\end{table}

@@

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r||c|c|}
        \hline
           Description    & mean F & std F \\
        \hline
           All            & 0.0    & 0.0   \\
           Just Stopwords & 0.0    & 0.0   \\
           Just Uncommon  & 0.0    & 0.0   \\
           Just Normalize & 0.0    & 0.0   \\
           Baseline       & 0.0    & 0.0   \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Performance of the Naive Bayes classifier using exhaustive
    cross-validation with 5 partitions}
    \label{table:bayes-results}
\end{table}

@@

% TODO finish table

@@

%TODO talk about the features

@@

>>>>

Number of features retained after feature selection varies from Tweet to Tweet.
To summarize the number of features retained after different process Table
\ref{table:numfeatures} presents the mean number of features per Tweet for
positive, neutral, negative examples as well as an overall average.

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|c||r|r|r|r|}
        \hline
        Description        & Positive & Neutral & Negative & Overall \\
        \hline
        All                & 14.85    & 14.06   & 15.10    & 14.49 \\
        Just Stopwords     & 17.13    & 16.86   & 17.41    & 17.04 \\
        Just Uncommon      & 18.43    & 17.87   & 18.85    & 18.21 \\
        Just Normalization & 19.65    & 19.16   & 20.06    & 19.46 \\
        Baseline           & 20.65    & 20.45   & 20.96    & 20.58 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{`Positive', `Neutral', `Negative', and `Overall' refer to the
    average number of features per Tweet in each experiment.}
    \label{table:numfeatures}
\end{table}

@@

The baseline for this project is established by running the Maximum Entropy
classifier without any stopword removal, uncommon word removal, Or feature
normalization. The F-score that is achieved is 50.72.

@@

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r||c|c|c|}
        \hline
        Description    & $\mu F$ & $\sigma F$ & $\delta\ \mu F$ \\
        \hline
        All            & \textbf{50.96} & 1.93 &  2.59 \\
        Just Stopwords & 48.27   & 1.83 & -0.10 \\
        Just Uncommon  & 49.02   & 1.96 &  0.65 \\
        Just Normalize & 49.55   & 2.10 &  1.18 \\
        Baseline       & 48.37   & 2.15 & - \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Performance of the Maximum Entropy classifier using exhaustive
    cross-validation with 5 partitions}
    \label{table:maxent-results}
\end{table}

@@

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r||c|c|c|}
        \hline
        Description    & $\mu F$ & $\sigma F$ & $\delta\ \mu F$ \\
        \hline
        All            & 49.28  & 0.81 &  1.17 \\
        Just Stopwords & 47.29  & 0.76 & -0.82 \\
        Just Uncommon  & 48.34  & 1.11 &  0.23 \\
        Just Normalize & \textbf{49.44} & 1.00 & 1.33\\
        Baseline       & 48.11  & 0.74 & - \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Performance of the Naive Bayes classifier using exhaustive
    cross-validation with 5 partitions}
    \label{table:bayes-results}
\end{table}

@@

@@

The implementation create for this project has the ability to show which
features are the most discriminatory. The following is a list of the top 30
most informative features from one run of the Maximum Entropy classifier:

@@

Some of the features listed above make perfect sense, such as `excited' not
being associated with the neutral class and `shitty' being associated with the
negative class. However some of the most discriminating features appear in the
dataset just enough to get past the uncommon word cutoff, such as `calvin' and
`oneil'.
